---
title: "AMICo algorithm"
author: "Johann R. Kleinbub"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The Adaptive Matching Interpolated Correlation (AMICo) is a dynamic time warping algorithm designed to infer the moment-by-moment synchronization between two skin conductance (SC) signals.

## Algorithm description
In synthesis, for each dyad the algorithm first identifies local maxima and minima (i.e., peaks and valleys) in the two SC signals. Then, it tries to match such features of one signal to those of the other (within a maximum lag) according to the solution that maximizes the similarity of each match across the whole session. 
A normally distributed weighting can be applied to penalize extreme lags.
Each of the two signals are then divided in segments ranging from a given matched feature to the one that follows after at least _minSizeSec_ seconds. The shorter of the two matched segments is then linearly interpolated to match the length of the longer one, in order to compare the shape of the two signals. The range of five seconds is required to have a sufficient number of data-points for each segment and was chosen from visual inspection of typical SC signals. Finally, Pearson correlation is calculated between every segment pair in the session. Results consist in a time-series of correlations, where each matched patient-therapist sequence is associated with one r value

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
